Model LF

### 2023-03-14 paper version Hamid test.Rmd
Commit

>>>>

```{r}
plot(window(max_dp_01 - max_dp_bs1, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(dp_person_01 - dp_person_bs1, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```
